### 2023-03-20 proofs/main.tex
Add contexts
Add lemmas overview + Various fixes
minor
Fix the definition of merge

\begin{definition}
  $[[us1 & us2]] = \{ [[usEntry1 & usEntry2]] \mid [[usEntry1]] \in [[us1]],
  [[usEntry2]]  \in [[us2]], \text{s.t. } [[usEntry1]] \text{ matches with } [[usEntry2]] \}$
\end{definition}

@@

@@

\subsection{Subtyping}

\input{../_build/_gen/tex/subtyping-lemmas.tex}

>>>>

\begin{definition}
  foo

  $\begin{aligned}[t]
  [[us1 & us2]] &= \{ [[usEntry1 & usEntry2]] \mid [[usEntry1]] \in [[us1]],
  [[usEntry2]]  \in [[us2]], \text{s.t. } [[usEntry1]] \text{ matches with }
                                   [[usEntry2]] \}\\
                &\cup
                                     \{ [[usEntry1]] \mid [[usEntry1]] \in
                                     [[us1]], \text{ s.t. }
                                     \forall [[usEntry2]]  \in [[us2]],
                                     [[usEntry1]] \text{ does not match with }
                                                     [[usEntry2]] \}\\
        &\cup
          \{ [[usEntry2]] \mid [[usEntry2]] \in
          [[us2]], \text{ s.t. }
          \forall [[usEntry1]]  \in [[us1]],
          [[usEntry1]] \text{ does not match with }
          [[usEntry2]] \}\\
   \end{aligned}$
\end{definition}

@@

\subsection{Overview}
\input{../_build/_gen/tex/lemmas-overview.tex}

@@

\subsection{Upper Bounds}

\input{../_build/_gen/tex/lub-lemmas.tex}
